\documentclass[11pt]{article}
\usepackage[margin=2.3cm]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{fancyhdr}
\usepackage{titlesec}
\definecolor{accent}{RGB}{40,90,140}
\definecolor{warn}{RGB}{150,60,30}
\definecolor{soft}{RGB}{95,100,110}
\allsectionsfont{\color{accent}\sffamily}
\titleformat{\section}{\Large\bfseries\sffamily\color{accent}}{\thesection}{0.6em}{}
\titleformat{\subsection}{\large\bfseries\sffamily\color{accent}}{\thesubsection}{0.5em}{}
\renewcommand{\arraystretch}{1.25}
\pagestyle{fancy}\fancyhf{}
\rhead{\sffamily\small\color{soft}2016 Ulsan-Fault picker-comparison pipeline}
\rfoot{\sffamily\small\color{soft}\thepage}
\setlength{\headheight}{14pt}
\newtcolorbox{keybox}[1]{colback=accent!6,colframe=accent!55,title=#1,fonttitle=\bfseries\sffamily,
  left=3mm,right=3mm,top=1.5mm,bottom=1.5mm}
\newtcolorbox{warnbox}[1]{colback=warn!6,colframe=warn!55,title=#1,fonttitle=\bfseries\sffamily,
  left=3mm,right=3mm,top=1.5mm,bottom=1.5mm}

\begin{document}

\begin{center}
{\huge\bfseries\sffamily\color{accent} 2016 Ulsan-Fault ML-picker comparison}\\[2mm]
{\large\sffamily A study guide: how the relocation pipeline runs, and what the four pickers show}\\[2mm]
{\small\color{soft} Detection $\rightarrow$ association $\rightarrow$ absolute location $\rightarrow$ QC $\rightarrow$ HypoDD dt.ct/dt.cc\hfill Consistent P{=}S{=}0.2 threshold}
\end{center}
\vspace{2mm}
\hrule
\vspace{4mm}

This document has two parts. \textbf{Part~1} walks the pipeline stage by stage so you can run and
audit it yourself, with the origin/location provenance made explicit (the place a subtle bug once
lived). \textbf{Part~2} is the corrected four-picker comparison and what it means scientifically.

%==================================================================================
\section{Part 1 — How the pipeline runs}

The engine is the \texttt{korea-cluster-relocation} pipeline (in \texttt{15.PocketQuake}), originally
built to relocate the KMA catalog. We feed our \emph{own} PhaseNet$+$/PyOcto catalog into it unchanged.
The \emph{only variable} across the four runs is the ML picker; every stage after picking is identical.

\begin{keybox}{The five invariants (keep these and the pipeline stays correct)}
\begin{enumerate}[leftmargin=6mm,itemsep=1mm]
\item \textbf{One HypoInverse solution, computed once, reused everywhere.} QC only \emph{selects} a
subset; it never re-locates. The subset relocation reuses the full-run \texttt{.sum}/\texttt{.arc}.
\item \textbf{Pick provenance is by \texttt{event\_idx}, never by timestamp.} An event's picks live in
\texttt{event\_sac/<event\_idx>/<event\_idx>\_picks.csv}. A time-window key can grab a neighbour's picks.
\item \textbf{Origins flow into dt.cc, not just into start locations.} \texttt{rereference} stamps SAC
origins from a \texttt{.sum}; xcorr then \emph{subtracts} them. A wrong \texttt{.sum} corrupts dt.cc values.
\item \textbf{\texttt{members.txt} row order defines the cuspid} ($200000+\text{row}$) tying together
\texttt{.sum}, \texttt{.arc}, \texttt{event.dat}, \texttt{dt.cc}. Never reorder without regenerating all.
\item \textbf{The catalog is fed in KST and round-trips to UTC.} Do not ``fix'' it to UTC (see box below).
\end{enumerate}
\end{keybox}

\subsection{The stages}

\begin{center}
\small
\begin{tabular}{@{}c>{\raggedright\arraybackslash}p{2.7cm}>{\raggedright\arraybackslash}p{5.3cm}>{\raggedright\arraybackslash}p{4.4cm}@{}}
\toprule
\# & Stage & In $\rightarrow$ Out & Origin/location source \\
\midrule
0 & Detection & continuous mSEED $\rightarrow$ \texttt{picks/*.parquet} & --- (raw picks, prob$\ge$0.2, P{=}S) \\
1 & Association (PyOcto) & picks $\rightarrow$ \texttt{catalog\_*\_pyocto.csv} + assign & \textbf{PyOcto} (rough). Gate 4/2/2, $\ge$1 P{+}S \\
2 & SAC store & assoc $\rightarrow$ \texttt{event\_sac/<idx>/*.sac} + \texttt{<idx>\_picks.csv} & PyOcto (in headers); \texttt{<idx>\_picks.csv} = true pick set \\
3 & UF-box catalog & $\rightarrow$ \texttt{catalog\_kma.csv} (KST), \texttt{members.txt} & defines cuspid $=200000+$row \\
4 & \textbf{Absolute loc (HypoInverse, FULL)} & assoc-pick \texttt{.arc} $\rightarrow$ \texttt{1.HypoInv/kim2011/*.sum} & \textbf{FULL-run HypoInverse = authoritative} \\
5 & \textbf{QC (filter only)} & full \texttt{.sum} $\rightarrow$ \texttt{members\_qc.txt} & \emph{no re-location} (see criteria below) \\
6 & Re-reference & \texttt{.sum} origins $\rightarrow$ restamp SAC \texttt{nz*}, \texttt{a}/\texttt{t0} & must read the full-run \texttt{.sum} \\
7 & ph2dt & \texttt{.arc} $\rightarrow$ \texttt{event.dat}, \texttt{dt.ct} & same \texttt{.arc} as stage 4/6 \\
8 & Cross-corr dt.cc (GPU) & re-ref SACs $\rightarrow$ \texttt{dt.cc\_0.7\_combined} & subtracts the stage-6 origins \\
9 & HypoDD & event.dat + dt.ct + dt.cc $\rightarrow$ \texttt{hypoDD.reloc} & relative reloc; ISTART=2, adaptive damping \\
\bottomrule
\end{tabular}
\end{center}

\noindent Driver: \texttt{run\_picker\_reloc.py --picker <p> --through dtcc} chains stages 2--9.

\subsection{The two quality gates}

\begin{center}
\small
\begin{tabular}{@{}ll@{\hskip 8mm}ll@{}}
\multicolumn{2}{@{}l}{\textbf{PyOcto association gate} (stage 1)} & \multicolumn{2}{l}{\textbf{HypoInverse QC} (stage 5, all must hold)} \\
\midrule
total picks & $\ge 4$ & \texttt{erh} & $<5$ km (horizontal error) \\
P picks & $\ge 2$ & \texttt{erz} & $<5$ km (depth error) \\
S picks & $\ge 2$ & \texttt{gap} & $<270^\circ$ (azimuthal gap) \\
P{+}S stations & $\ge 1$ & \texttt{num} & $>5$ ($\ge$6 phases) \\
velocity & kim2011 1-D & \texttt{rms} & $<1.0$ s (residual RMS) \\
\end{tabular}
\end{center}

The association gate is deliberately \emph{permissive}; the real quality control is the HypoInverse QC.
HypoDD uses kim2011, ISTART=2 (mainshock fixed), and adaptive LSQR damping (condition number kept
$\sim$40--80). ``dt.cc-resolved'' = an event keeping $\ge 1$ surviving cross-correlation link
(\texttt{nccp{+}nccs}$>0$) --- the highest-precision subset.

\begin{warnbox}{Why the catalog is ``\texttt{catalog\_kma.csv}'' and in KST (a common confusion)}
We do \textbf{not} use the KMA catalog. The pipeline hard-codes \texttt{kst\_offset\_hours = 9}
($\text{origin}_\text{UTC} = \text{catalog}_\text{KST} - 9\text{h}$). So \texttt{build\_catalog\_kma.py}
converts our PyOcto \emph{UTC} origins to KST ($+9$h) \emph{only so the pipeline subtracts 9\,h again} and
lands back on the true UTC origin --- a deliberate \textbf{no-op round-trip} to satisfy the pipeline's
KST-input contract. \texttt{catalog\_kma.csv} is a \emph{format label}, not a data source. Feeding UTC
directly would place every event 9\,h in the past.
\end{warnbox}

\subsection{The bug that was fixed (a worked example of the invariants)}

The QC$\rightarrow$dt.cc chain used to scaffold a \emph{separate} QC cluster and \textbf{re-run
HypoInverse + ph2dt} on it (violating invariant~1). That re-run re-staged picks by a second-resolution
\emph{timestamp} key (violating invariant~2), so on dense catalogs an adjacent event's raw picks
overwrote the correct associated picks $\rightarrow$ wrong origins (up to $\sim$1\,s off). Those wrong
origins then poisoned \texttt{rereference} $\rightarrow$ \textbf{dt.cc values} (invariant~3) and
\texttt{event.dat}/\texttt{dt.ct}. \emph{Symptom that exposed it:} \texttt{event.sel} showed
$\text{ERZ}>5$\,km events that had passed QC --- because those errors came from the re-run, not the full
run QC gated on. \textbf{Fix:} inject the full-run HypoInverse (\texttt{.sum}/\texttt{.arc}) subset to the
QC members, then re-run rereference$\rightarrow$ph2dt$\rightarrow$xcorr$\rightarrow$dtcc against correct
origins. One HypoInverse solution, reused (now permanent in
\texttt{run\_picker\_reloc.py::inject\_full\_hypoinverse}).

\subsection{Reproducing the output yourself (run these in order)}

All commands run from \texttt{Gyeongju\_catalog/detection\_test/}. The picker \texttt{<p>} is one of
\texttt{original}, \texttt{stead}, \texttt{eqt} (PN$+$ is already done and is reused). \texttt{<Y>} is the year
(\texttt{2016} here). Stages A--C are \emph{per month}; loop \texttt{<mm>} over \texttt{01}..\texttt{12}. Stage
0 checks readiness; Stage D chains everything association-onward for one picker.

\begin{center}
\small
\begin{tabular}{@{}c>{\raggedright\arraybackslash}p{3.3cm}>{\ttfamily\raggedright\arraybackslash}p{9.6cm}@{}}
\toprule
& Step & \normalfont command \\
\midrule
0 & Readiness check (per year) & python reloc\_2016\_uf/preflight\_year.py -{}-year <Y> \\
\midrule
A & Station cache (per month) & python lib/build\_stations.py -{}-month <Y>-<mm> \\
B & Detection (per picker, per month) & python lib/run\_seisbench\_picker.py -{}-model <p> -{}-month <Y>-<mm> \\
  & \quad (PN$+$: \texttt{run\_pnplus\_month.py}) & \\
C & Association (per picker, per month) & python lib/associate\_daily.py -{}-picker <p> -{}-month <Y>-<mm> \\
\midrule
D & \textbf{Relocation chain} (once per picker) & python reloc\_2016\_uf/run\_picker\_reloc.py -{}-picker <p> -{}-year <Y> -{}-through dtcc \\
\midrule
E & Comparison notebooks & jupyter nbconvert -{}-execute -{}-inplace \\
  & & \quad reloc\_2016\_uf/10.Picker\_comparison\_2016.ipynb \\
\bottomrule
\end{tabular}
\end{center}

\noindent\textbf{What stage D does internally} (stages 2--9 of the table above): builds the event-idx SAC
store $\rightarrow$ \texttt{catalog\_kma}/\texttt{members} $\rightarrow$ scaffold $+$ HypoInverse (full)
$\rightarrow$ \texttt{uf\_cluster} QC $\rightarrow$ \emph{inject the full-run HypoInverse into the QC
subset} (the fix) $\rightarrow$ rereference $\rightarrow$ ph2dt $\rightarrow$ GPU xcorr
(\texttt{interp\_hz}=1000, run in the \texttt{pq-gpu} conda env) $\rightarrow$ adaptive kim2011/ISTART=2
HypoDD. Stop earlier with \texttt{-{}-through hypoinverse} to validate the chain up to QC (fast).

\begin{keybox}{Practical notes}
\begin{itemize}[leftmargin=5mm,itemsep=0.5mm]
\item Detection is CPU/IO-bound (GPU $\sim$27\,\%) --- run the three pickers' months concurrently ($\sim$3$\times$).
\item The dt.cc xcorr is the long pole: $\sim$6\,h each for the dense pickers (PN$+$ 177\,k pairs,
original 164\,k); STEAD/EQT are minutes. It is checkpointable (\texttt{XCORR\_RESUME=1}).
\item Everything is idempotent / safe to re-run; the QC injection backs up any prior HypoInverse to
\texttt{1.HypoInv/kim2011.rerun\_backup}.
\end{itemize}
\end{keybox}

\subsection{Does this inherit to every year 2010--2025 without adjustment?}

\textbf{Yes --- the whole chain is \texttt{-{}-year} general, and robust to network/rate change by design.}
Every layer is year-parameterized; the ones below marked ``auto'' need \emph{no} per-year adjustment.

\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{3.6cm}cccc>{\raggedright\arraybackslash}p{4.3cm}@{}}
\toprule
Layer & Year? & Network? & Rate? & Ad hoc? & How \\
\midrule
Station cache \newline (\texttt{build\_stations.py}) & \texttt{-{}-month} & \textbf{auto} & --- & no & epochs/coords/bands read from StationXML; \texttt{coverage} = days on disk $\Rightarrow$ picks up whatever is deployed \\
Detection \newline (\texttt{run\_seisbench\_picker.py}) & \texttt{-{}-month} & \textbf{auto} & \textbf{auto} & no & anti-alias decimate per station; runs 2014/2016/2021 already \\
Association \newline (\texttt{associate\_daily.py}) & \texttt{-{}-month} & \textbf{auto} & --- & no & daily-chunked PyOcto; same fixed 4/2/2 gate every epoch \\
SAC store \newline (\texttt{event\_sac\_export}) & --- & \textbf{auto} & \textbf{native} & no & \texttt{SAC\_TARGET\_HZ=None} keeps native rate; xcorr interpolates at correlation time \\
\textbf{Orchestration} \newline (\texttt{run\_picker\_reloc.py}) & \textbf{\texttt{-{}-year}} & auto & auto & no & all year-dependent names via \texttt{year\_paths.py}; \texttt{-{}-year 2016} = the exact existing paths \\
\bottomrule
\end{tabular}
\end{center}

\noindent\textbf{Robustness to network/rate change is built in, no tuning.} Network change (KS/KG only in 2010
$\rightarrow$ $+$NS dense array 2017$+$ $\rightarrow$ $+$GJ temporary 2016) is handled automatically because
stations are \emph{discovered from metadata $+$ on-disk coverage each month}, not listed. Sampling-rate change
(100 / 200 / 1000\,Hz across KS/KG/NS/GJ) is handled by the \emph{native-rate} SAC store plus
interpolate-at-correlation-time --- this was the specific fix for the GJ mixed-rate loss. The velocity model
(kim2011), QC thresholds, and the 4/2/2 gate are epoch-invariant by choice, so catalogs stay directly
comparable across years. Archive coverage confirms the data exists and the network grows: 2010 has
$\sim$2\,300 KS/KG station-days, 2022 $\sim$5\,900.

\begin{keybox}{Running any year (the orchestration is done)}
\texttt{year\_paths.py} centralizes every year-dependent name; \texttt{-{}-year} defaults to 2016 and resolves
to the exact existing 2016 paths/slugs, so 2016 work is byte-unchanged. Naming: \texttt{reloc\_<Y>\_uf[\_<p>]/},
slug \texttt{uf\_<Y>[\_<p>]}, \texttt{stations\_<Y>.csv}. To run a year:\\[1mm]
\hspace*{3mm}\texttt{python preflight\_year.py -{}-year <Y>}\hfill (which inputs exist / what to run)\\
\hspace*{3mm}\texttt{python run\_picker\_reloc.py -{}-picker <p> -{}-year <Y> -{}-through dtcc}\\[1mm]
\textbf{What a new year still needs:} only its Stage 0--1 \emph{inputs} generated (detection $+$ association for
the 12 months --- the heavy compute); the orchestration (Stages 2--9) then runs unchanged. \emph{Real} per-year
effects, none requiring code changes: network-gap months give smaller sets; sparse early years (2010--2012,
KS/KG only) have larger azimuthal gaps so fewer events survive QC (the gate correctly reflects this rather than
inventing precision); the dt.cc xcorr cost scales as $O(N^2)$ in events, so dense aftershock years are the
expensive ones. These are the pipeline honestly reporting what each year's network resolves.
\end{keybox}

%==================================================================================
\section{Part 2 — The four-picker comparison (corrected)}

Four ML pickers, one pipeline, consistent P{=}S{=}0.2 threshold. The question is not who \emph{picks}
most, but who yields the most well-located, cross-correlation-resolved events.

\subsection{The funnel: picks $\rightarrow$ region events $\rightarrow$ UF-box $\rightarrow$ QC $\rightarrow$ dt.cc $\rightarrow$ dt.cc-resolved}

\begin{center}
\small
\begin{tabular}{@{}lrrcrrrrr@{}}
\toprule
picker & P picks & S picks & S/P & region ev. & UF-box & QC & dt.cc & \textbf{cc-res.} \\
\midrule
\textbf{PN+}          & 533\,394 & 638\,063 & 1.20 & 28\,168 & 3\,867 & 596 & 512 & \textbf{255} \\
PN-original           & 951\,731 & 839\,799 & 0.88 & 31\,762 & 4\,117 & 574 & 447 & 189 \\
PN-STEAD              & 122\,744 & 227\,351 & 1.85 &  6\,472 &   398 & 188 & 172 & 103 \\
EQT-STEAD             &  87\,396 &  95\,638 & 1.09 &  6\,540 &   424 & 160 & 144 &  92 \\
\bottomrule
\end{tabular}
\end{center}

\noindent\textbf{How to read each column.} \emph{Picks} = raw detections (whole year, whole region).
\emph{Region ev.} = all PyOcto-associated events. \emph{UF-box} = events inside the fault box (relocation
members). \emph{QC} = pass the HypoInverse quality gate. \emph{dt.cc} = HypoDD-relocated with cross-corr.
\emph{cc-res.} = keep $\ge 1$ surviving cc link --- the headline, highest-precision number.

\subsection{Fingerprints and headline}

\begin{itemize}[leftmargin=6mm,itemsep=1mm]
\item \textbf{Pick quantity does not predict located quality.} PN-original picks the \emph{most}
(1.79\,M) and associates the most region events (31\,762), yet yields the \emph{fewest} cc-resolved of
the two PN models (189 vs PN+'s 255). Raw detection is an association liability when it is noisy.
\item \textbf{S/P ratio is a picker fingerprint:} PN-original is P-heavy (0.88), PN-STEAD strongly
S-heavy (1.85), PN+ balanced (1.20), EQT (1.09). The 4/2/2 gate rebalances this downstream.
\item \textbf{A fixed 0.2 threshold is not equivalent across pickers.} The STEAD-retrained models
(PN-STEAD, EQT) are far more conservative at 0.2 than NCEDC/EQNet (PN-original, PN+): $\sim$6\,\% of their
region events fall in the UF box vs $\sim$13\,\% for the PN models.
\item \textbf{Headline: PN+ delivers the most cross-correlation-resolved, well-located events (255)}
despite not picking the most --- the best balance of sensitivity and pick quality.
\end{itemize}

\subsection{Why PN-original \emph{dropped} after the fix (463$\rightarrow$447; cc-res.\ 212$\rightarrow$189)}

This is the fix working, not a regression. The dt.cc value is
$\;dt = (t_1+\text{shift}-ot_1) - (t_2-ot_2)$; the cross-correlation \emph{coefficient} (which gates the
0.7 cut) is origin-independent, but the stored \emph{value} carries the origins $ot$. PN-original, the
noisiest picker, had the \emph{largest} origin errors in the buggy run (\textbf{median 0.13\,s; 121
events off by $>$0.5\,s; 59 by $>$1\,s}, vs PN+'s median 0.07\,s). A \emph{systematic per-event} offset
is partly absorbable by relocating the event, so those links \emph{survived} HypoDD's residual cuts
(\texttt{WDCC} $= 6,4,3,2\rightarrow0.5$\,s across the iteration sets) --- keeping the event
``cc-resolved'' but at a wrong, offset-driven position. With the origins corrected, the truly
inconsistent links show their real (large) residuals and are \emph{correctly rejected}; events losing all
cc links fall to ct-only, and marginal ones may not relocate. Hence a \textbf{smaller but genuinely
better-located} set --- confirmed by the relative error \emph{improving} $0.72\rightarrow0.50$\,m. PN+
barely moved ($251\rightarrow255$) precisely because its origin errors were small.

\begin{keybox}{One-sentence takeaway}
The buggy origin offsets were coherent enough to be absorbed as fake relocations that passed HypoDD's
residual cuts; correcting the origins exposes the truly-inconsistent links, which HypoDD then correctly
rejects --- so PN-original's count drops but its catalog becomes more trustworthy.
\end{keybox}

\subsection{Corrected vs.\ buggy (all four)}

\begin{center}
\small
\begin{tabular}{@{}lccc@{\hskip 8mm}cc@{}}
\toprule
& \multicolumn{3}{c}{\textbf{corrected} / buggy} & \multicolumn{2}{c}{origin error (buggy)} \\
\cmidrule(lr){2-4}\cmidrule(l){5-6}
picker & dt.cc total & cc-resolved & rel-err (m) & median & \#$>$0.5\,s \\
\midrule
PN+          & 512 / 511 & \textbf{255} / 251 & 0.42 / 0.42 & 0.07\,s & few \\
PN-original  & 447 / 463 & \textbf{189} / 212 & \textbf{0.50} / 0.72 & 0.13\,s & 121 \\
PN-STEAD     & 172 / 172 & \textbf{103} / 116 & 0.36 / 0.28 & small & 8 \\
EQT-STEAD    & 144 / 146 & \textbf{92}  / 101 & 0.42 / 0.28 & small & 6 \\
\bottomrule
\end{tabular}
\end{center}

\noindent All four have \textbf{zero air-quakes} (no depth $<0$ or $>30$\,km) and healthy adaptive-damping
convergence. The magnitude of each picker's change tracks its origin-error magnitude: PN-original (worst
corruption) moves most; PN+ (least) barely moves.

\vspace{3mm}\hrule\vspace{2mm}
{\small\color{soft} Companion files: \texttt{PIPELINE.md} (invariants + provenance checks),
notebooks \texttt{09/10/12} (comparison, funnel, record sections),
\texttt{run\_picker\_reloc.py} $+$ \texttt{year\_paths.py} $+$ \texttt{preflight\_year.py} (year-general driver),
\texttt{fix\_qc\_rerun\_bug.py} (the repair driver).}

\end{document}
