\documentclass[11pt]{article}
\usepackage[margin=2.2cm]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}
\definecolor{accent}{RGB}{40,90,140}
\definecolor{warn}{RGB}{150,60,30}
\definecolor{soft}{RGB}{95,100,110}
\allsectionsfont{\color{accent}\sffamily}
\titleformat{\section}{\Large\bfseries\sffamily\color{accent}}{\thesection}{0.6em}{}
\titleformat{\subsection}{\large\bfseries\sffamily\color{accent}}{\thesubsection}{0.5em}{}
\renewcommand{\arraystretch}{1.25}
\pagestyle{fancy}\fancyhf{}
\rhead{\sffamily\small\color{soft}ufpipe — Ulsan-Fault catalog pipeline reference}
\rfoot{\sffamily\small\color{soft}\thepage}
\setlength{\headheight}{14pt}
\newtcolorbox{keybox}[1]{colback=accent!6,colframe=accent!55,title=#1,fonttitle=\bfseries\sffamily,
  left=3mm,right=3mm,top=1.5mm,bottom=1.5mm}
\newtcolorbox{warnbox}[1]{colback=warn!6,colframe=warn!55,title=#1,fonttitle=\bfseries\sffamily,
  left=3mm,right=3mm,top=1.5mm,bottom=1.5mm}
\newcommand{\code}[1]{\texttt{#1}}
% let long typewriter paths break inside words so they don't overflow the right margin
\usepackage{url}
\sloppy
\emergencystretch=3em

\begin{document}

\begin{center}
{\huge\bfseries\sffamily\color{accent} Ulsan-Fault earthquake catalog pipeline}\\[2mm]
{\large\sffamily Reference manual: detection $\rightarrow$ association $\rightarrow$ location $\rightarrow$ relocation (HypoDD dt.ct + dt.cc)}\\[2mm]
{\small\color{soft} Long-term (2010–present) catalog for the Ulsan Fault, SE Korea\hfill rev.\ 2026-07-24 · \code{src/ufpipe}}
\end{center}
\vspace{1mm}\hrule\vspace{3mm}

{\small \code{ufpipe} (\code{src/ufpipe}) is the \textbf{end-to-end pipeline}: six stages, detection $\rightarrow$
association $\rightarrow$ augment $\rightarrow$ PHS $\rightarrow$ locate $\rightarrow$ \textbf{relocate} (HypoDD
dt.ct $+$ dt.cc). The final \code{relocate} stage produces the double-difference relocated catalog. The heavy
dt.cc/xcorr/HypoDD \emph{engine} is external (\code{15.PocketQuake} korea-cluster-relocation, HypoDD v2.1beta);
ufpipe orchestrates it. The relocate stage is \textbf{self-fed}: it builds its inputs from ufpipe's OWN
detection+association (\code{ufpipe.reloc\_inputs}) and runs the orchestration in
\code{src/ufpipe/reloc\_driver/}; working dirs + results go to \code{outputs/reloc/}.
\code{detection\_test/} is a \textbf{fully frozen pilot archive} (the 2016 4-picker comparison;
\code{lib/} DEPRECATED, see \code{detection\_test/lib/DEPRECATED.md}). The relocation internals have a
dedicated guide: \code{src/ufpipe/reloc\_driver/PIPELINE.md} + the pilot's \code{study\_guide.pdf}.}

\tableofcontents
\vspace{3mm}\hrule

%================================================================================
\section{What the pipeline does}

Build an \textbf{internally consistent, long-term earthquake catalog} for the Ulsan Fault region (SE Korea),
2010–present, from continuous seismic waveforms, using AI phase pickers so small events are detected uniformly
even as the recording network grows, and finally \textbf{relocate} the catalog with double-difference (HypoDD
dt.ct + dt.cc) for sub-100\,m relative precision. Every stage is scripted and parameterized; results reproducible.

\begin{center}
\small
\begin{tabular}{@{}ccccc@{}}
\textbf{Detection} & \textbf{Association} & \textbf{Location} & \textbf{QC} & \textbf{Relocation} \\
PhaseNet / PhaseNet+ & PyOcto (+augment) & HYPOINVERSE & \code{uf\_cluster} & HypoDD dt.ct + dt.cc \\
\emph{picks} $\rightarrow$ & \emph{events+assign} $\rightarrow$ & \emph{.sum/.arc} $\rightarrow$ & \emph{well-located} $\rightarrow$ & \emph{hypoDD.reloc} \\
\end{tabular}
\end{center}

\subsection{\code{ufpipe} vs \code{detection\_test}}
\code{ufpipe} is the production end-to-end pipeline; everything live is under \code{src/}, including the
relocation orchestrator \code{src/ufpipe/reloc\_driver/run\_picker\_reloc.py} (driven by the relocate stage
with \code{-{}-skip-build}; the HypoDD/xcorr engine itself is external in \code{15.PocketQuake}).
\code{detection\_test} is the \textbf{frozen pilot archive} of the 2016 4-picker comparison — nothing in it
is live (\code{lib/} DEPRECATED; the \code{reloc\_2016\_uf*/} dirs hold the pilot's manifests and results).
\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{5.6cm}>{\raggedright\arraybackslash}p{5.7cm}@{}}
\toprule
 & \textbf{\code{ufpipe}} (\code{src/ufpipe}) & \textbf{\code{detection\_test}} \\
\midrule
Role & the self-contained end-to-end catalog + relocation pipeline (incl.\ \code{reloc\_driver/}) & frozen archive of the 2016 4-picker pilot \\
Stages & detection $\rightarrow$ association $\rightarrow$ augment $\rightarrow$ PHS $\rightarrow$ locate $\rightarrow$ \textbf{relocate} & --- (nothing live) \\
Driver & \code{python -m ufpipe.run\_pipeline} & --- \\
Ends at & HypoDD dt.cc (\S7); results in \code{outputs/reloc/} & --- \\
\bottomrule
\end{tabular}
\end{center}
ufpipe's own detection + association cover \textbf{KS/KG/GJ/NS} with daily-chunked association (\S5), and the
\code{relocate} stage builds its inputs from those outputs (\code{ufpipe.reloc\_inputs}); it no longer consumes
\code{detection\_test/lib}. The pipeline is fully self-contained. See \S7.

\subsection{Two orthogonal ``model'' dimensions}
\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
Dimension & Flag & Values \\
\midrule
\textbf{Picker model} & \code{-{}-model} & \code{stead}, \code{original}, \code{phasenet\_plus}, \code{eqt}, \dots \\
\textbf{Velocity model} & \code{-{}-velmodel} & \code{kim1983}, \code{kim2011} \\
\bottomrule
\end{tabular}
\end{center}
Any picker model can be located with any velocity model. \code{stead}/\code{original} are SeisBench PhaseNet
weights; \code{phasenet\_plus} is EQNet PhaseNet+ (needs a local EQNet clone).

%================================================================================
\section{Install \& environment}

The pipeline runs in a \textbf{two-env split} on this server (there is no single ``ulsan'' env):
detection (PhaseNet+/SeisBench, torch) in \code{eqnet} (Py 3.9); association (PyOcto) + orchestration in
\code{base} (Py 3.12); the relocate stage's GPU xcorr shells out to \code{pq-gpu} internally.

\begin{keybox}{One-time setup}
\begin{enumerate}[leftmargin=6mm,itemsep=0.5mm]
\item \code{conda run -n eqnet pip install -e . -{}-no-deps} \hfill(detection env)
\item \code{conda run -n base~ pip install -e . -{}-no-deps} \hfill(association/orchestration env)
\item \textbf{HYPOINVERSE}: the external \code{hyp1.40} binary must be on \code{PATH} (not pip-installable).
\item \textbf{PhaseNet+ only}: a local EQNet clone at \code{config.EQNET\_DIR}.
\item \textbf{Fresh machine}: \code{conda env create -f environment.yml} (env \code{uf-catalog}), then install the
      torch build matching your CUDA (\code{pip install torch -{}-index-url https://download.pytorch.org/whl/cu128}).
\end{enumerate}
\end{keybox}

After \code{pip install -e .}, \code{import ufpipe.config} and \code{python -m ufpipe.run\_pipeline} work from any
directory — no \code{sys.path} hacks.

%================================================================================
\section{Stages 1--5: detection through location}

\code{STAGES = [detection, association, augment, phs, locate, relocate]} — run in order. Stages 1--5 (below) are
functions in \code{src/ufpipe/core.py}; the relocate stage (6) is \code{src/ufpipe/relocate.py} and has its own
\S7. \code{run\_pipeline.py} chains them per year.

\begin{center}
\small
\begin{longtable}{@{}c>{\raggedright\arraybackslash}p{2.4cm}>{\raggedright\arraybackslash}p{5.0cm}>{\raggedright\arraybackslash}p{5.2cm}@{}}
\toprule
\# & Stage & In $\rightarrow$ Out & What it does \\
\midrule
\endhead
1 & \textbf{detection} & continuous mSEED $\rightarrow$ \code{picks/} (per station-day) & AI picker on each station-day across \textbf{KS/KG/GJ/NS} (per-year multi-network table, \code{stations.py}); anti-alias $>$100 Hz, unify mixed rates, resample to 100 Hz, pick P/S above threshold. GPU. Idempotent (skips done days). \\
2 & \textbf{association} & picks $\rightarrow$ \code{pyocto\_*.csv} + assignment & PyOcto octree associator groups picks into events (gate below), \textbf{daily-chunked} ($\pm$150 s/day, in-day origins) so it scales to the dense NS array. Coords from the multi-network table. \\
3 & \textbf{augment} & assignment $\rightarrow$ augmented assignment & scan daily picks for orphans PyOcto missed, add to each event so HYPOINVERSE sees the full pick set. Backs up + overwrites in place; idempotent. \\
4 & \textbf{phs} & assignment $\rightarrow$ \code{UF\{year\}.phs} & write the HYPOINVERSE phase file from the (augmented) assignment. \\
5 & \textbf{locate} & \code{.phs} $\rightarrow$ \code{UF\{year\}.\{sum,arc\}} & run HYPOINVERSE (\code{hyp1.40}) with the chosen velocity model $\rightarrow$ located catalog + errors. \\
\bottomrule
\end{longtable}
\end{center}

\begin{warnbox}{Pipeline order matters}
\code{augment} runs \emph{between} \code{association} and \code{phs}, so HYPOINVERSE sees the full augmented pick
set and computes correct \code{GAP}/\code{DMIN}/\code{ERZ}/\code{RMS}. Do not reorder.
\end{warnbox}

\subsection{Source of truth for pick$\leftrightarrow$event assignment}
The \textbf{PyOcto assignment (after augmentation)} is authoritative for which \code{(station, phase)} tuples
belong to each event. Do NOT use a legacy time-window pick dump — when two events fall $<$60\,s apart at the same
station the earliest pick ``wins'' and leaks into the wrong event. Downstream (SAC-header writers, magnitude/QC
notebooks) must read \code{pyocto\_assignment\_\{velmodel\}\_\{year\}.csv}.

%================================================================================
\section{Parameters (\code{src/ufpipe/config.py} — the single disclosed source)}

Change defaults here. Everything is one file.

\subsection{Detection / DSP}
\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{3.6cm}>{\raggedright\arraybackslash}p{4.0cm}>{\raggedright\arraybackslash}p{6.6cm}@{}}
\toprule
Parameter & Value & Meaning \\
\midrule
\code{SAMPLING\_RATE} & 100.0 Hz & the pickers' trained rate; all data resampled to it \\
\code{ANTIALIAS} & lowpass 45 Hz, 8 corners, zerophase & applied BEFORE down-sampling ($>$100 Hz KG/NS) \\
\code{BANDPASS} & 1--40 Hz, 4 corners, causal & legacy detection path; PhaseNet+ runs raw \\
\code{P\_THRESHOLD}, \code{S\_THRESHOLD} & 0.2 & SeisBench pick probability threshold \\
\code{PNPLUS\_MIN\_PROB} & 0.3 & EQNet PhaseNet+ pick threshold \\
\code{PNPLUS\_NT} & $1024{\times}36$ & PhaseNet+ patch length (whole-day, \code{cut\_patch}) \\
\code{MAX\_CORES} & 24 & CPU cap (respects \code{taskset} affinity) \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Association (PyOcto) — daily-chunked, \code{ASSOC\_GATE} (lenient) vs \code{ASSOC\_GATE\_STRICT}}
Association runs \textbf{one calendar day at a time}: a $\pm$\code{ASSOC\_OVERLAP\_S} (150 s) window per day is
associated and only events whose \emph{origin} falls in-day are kept (dedup). This is physically equivalent to a
single pass (local events are seconds long) but keeps each PyOcto solve to seconds --- a whole-year single pass is
intractable on the dense $\sim$200-station NS array ($\gg$1 h, 12 GB). Station coordinates come from the
multi-network year table (\code{stations.py}), so KS/KG/GJ/NS all associate.
\begin{center}
\small
\begin{tabular}{@{}lcc l@{}}
\toprule
Parameter (\code{config}) & lenient & \code{\_STRICT} & Meaning \\
\midrule
\code{REGION\_CENTER} $\pm$ pad & \multicolumn{2}{c}{(35.856,129.224) $\pm$ (1.0,1.2)} & search area (deg) \\
\code{ASSOC\_ZLIM} & \multicolumn{2}{c}{(0, 30)} & depth range (km) \\
\code{ASSOC\_TIME\_BEFORE} & \multicolumn{2}{c}{300} & origin-search window (s) \\
\code{ASSOC\_OVERLAP\_S} & \multicolumn{2}{c}{150} & daily-chunk overlap (s) \\
\code{n\_picks} & 4 & 6 & min total picks \\
\code{n\_p} / \code{n\_s} & 2 / 2 & 3 / 3 & min P / S picks \\
\code{n\_ps} & 1 & 2 & min stations with both P+S (depth) \\
\code{ASSOC\_PICK\_MATCH\_TOL} & \multicolumn{2}{c}{1.5} & residual cap (s) \\
\bottomrule
\end{tabular}
\end{center}
Pass \code{-{}-strict} to use \code{ASSOC\_GATE\_STRICT} (fewer, cleaner events). \code{-{}-workers N} parallelises
the independent daily chunks. Velocity for association = \code{ASSOC\_VELMODEL} (\code{kim2011} 1-D), matching the
reloc feeder. Output schema (events \code{idx,time,x,y,z,picks,latitude,longitude,depth}; assignment
\code{event\_idx,pick\_idx,residual,station,phase,time}) is unchanged, so \code{phs}/\code{locate}/\code{relocate}
consume it as before.

\subsection{Velocity model \& location}
\code{DEFAULT\_VELMODEL = kim2011}; \code{kim1983} also available (\code{data/metadata/velocity/kim1983.csv},
a layered $V_p$/$V_s$ model; HYPOINVERSE \code{*.crh} tables live in \code{data/hypoinv/\{kim1983,kim2011\}/}).
\code{PHASE\_CHANNELS = \{P: HHZ, S: HHN\}}.

%================================================================================
\section{How to run}

\begin{keybox}{Standard runs (from the repo root)}
\begin{tabular}{@{}>{\ttfamily}p{8.4cm}>{\raggedright\arraybackslash}p{6.2cm}@{}}
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2024 & one year, all 5 stages \\
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2010-2024 & the whole record \\
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2015,2016 -{}-velmodel kim1983 & specific years, kim1983 \\
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2024 -{}-stage-from association & resume (picks already done) \\
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2024 -{}-days 1-3 & detection on a few days (testing) \\
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2024 -{}-strict & strict association gate \\
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2016 -{}-stage-from relocate -{}-through dtcc & relocation only (dt.cc; needs feeder) \\
\end{tabular}
\end{keybox}

\noindent\textbf{CLI flags:} \code{-{}-model} · \code{-{}-years} (\code{'2010-2024'} or \code{'2015,2016'}) ·
\code{-{}-velmodel} · \code{-{}-days} · \code{-{}-device \{cuda,cpu\}} · \code{-{}-workers} · \code{-{}-strict} ·
\code{-{}-force} (allow writing to \code{stead}) ·\\ \code{-{}-stage-from
\{detection,association,augment,phs,locate\}} (start mid-chain).

\begin{warnbox}{Shared 64-core server — always pin cores}
Detection sizes its preprocessing pool and \code{torch} threads from the process CPU \emph{affinity}, capped by
\code{MAX\_CORES=24}. Launch under \code{taskset} so the whole job stays within budget:\\[1mm]
\hspace*{3mm}\code{OMP\_NUM\_THREADS=1 taskset -c 0-7 python -m ufpipe.run\_pipeline -{}-model original -{}-years 2010-2024}\\[1mm]
Without pinning, PhaseNet+ grabbed $\sim$49 cores / 193 threads and starved everything. Inference is
\textbf{GPU-preferred} (warns loudly, never silently falls back to CPU).
\end{warnbox}

\noindent Detection is \textbf{idempotent} — it skips station-days whose picks already exist, so runs resume
safely after an interruption.

\subsection{Running each stage separately}
Every \code{ufpipe} stage is also a standalone CLI (\code{-{}-model -{}-year}), so you can run detection alone,
then association alone, etc. Order is \code{detection $\rightarrow$ association $\rightarrow$ augment
$\rightarrow$ phs $\rightarrow$ locate}. Each reads the previous stage's output from disk.

\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{2.4cm}>{\ttfamily\raggedright\arraybackslash}p{12.0cm}@{}}
\toprule
Stage & \normalfont standalone command \\
\midrule
Detection & python -m ufpipe.detection -{}-model original -{}-year 2024 [-{}-networks KS,KG,GJ,NS] [-{}-days 1-5] [-{}-workers 8] \\
Association & python -m ufpipe.association -{}-model original -{}-year 2024 [-{}-networks KS,KG,GJ,NS] [-{}-workers 8] [-{}-strict] \\
Augment & \normalfont(runs inside \code{run\_pipeline}; or call \code{core.run\_augment\_year} from Python) \\
PHS & python -m ufpipe.make\_phs -{}-model original -{}-year 2024 \\
Location & python -m ufpipe.run\_hypoinverse -{}-model original -{}-year 2024 -{}-velmodel kim2011 \\
\bottomrule
\end{tabular}
\end{center}

Or drive the same stage functions from Python / a notebook:
\begin{quote}\small\ttfamily
from ufpipe import core, config\\
core.run\_detection\_year("original", 2024, days=range(1,6))\\
events, assign = core.run\_association\_year("original", 2024)\\
core.write\_phs("original", 2024); core.run\_hypoinverse\_year("original", 2024, velmodel="kim2011")
\end{quote}

\subsection{Relocation — running the last stage (stage 6)}
The relocate stage is \textbf{self-fed}: it needs only ufpipe's own per-year detection + association
(\code{pyocto\_kim2011\_<year>.csv} + assignment). It builds the reloc input store (event-idx SAC + station table)
from those via \code{ufpipe.reloc\_inputs}, then hands off to the driver \code{run\_picker\_reloc.py -{}-skip-build}
(scaffold $\rightarrow$ HYPOINVERSE $\rightarrow$ QC $\rightarrow$ rereference $\rightarrow$ GPU xcorr $\rightarrow$
HypoDD dt.cc). If a year's association is missing, the stage preflights and prints exactly what to run.

\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{2.9cm}>{\ttfamily\raggedright\arraybackslash}p{11.5cm}@{}}
\toprule
Step & \normalfont command \\
\midrule
Detection & conda run -n eqnet python -m ufpipe.detection -{}-model original -{}-year 2016 \\
Association & conda run -n base python -m ufpipe.association -{}-model original -{}-year 2016 \\
Reloc (to QC) & python -m ufpipe.run\_pipeline -{}-model original -{}-years 2016 -{}-stage-from relocate -{}-through hypoinverse \quad\normalfont(fast) \\
Reloc (full) & python -m ufpipe.run\_pipeline -{}-model original -{}-years 2016 -{}-stage-from relocate -{}-through dtcc \quad\normalfont(+ xcorr$\rightarrow$HypoDD dt.cc; $\sim$6\,h dense) \\
\bottomrule
\end{tabular}
\end{center}
\code{-{}-through hypoinverse} stops at the QC'd absolute-location subset; \code{-{}-through dtcc} continues to the
double-difference relocation. \code{-{}-clean-cache} deletes the $\sim$tens-of-GB interp cache after dt.cc
(essential for multi-year runs). \code{detection\_test/lib/} is DEPRECATED (see \code{lib/DEPRECATED.md}); the
relocation internals are documented in \code{src/ufpipe/reloc\_driver/PIPELINE.md} + \code{study\_guide.pdf}.

%================================================================================
\section{Outputs \& layout}

All pipeline products go under \code{outputs/models/<model>/} (regenerable; gitignored):
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
Path & Contents \\
\midrule
\code{.../detection\_location/<year>/picks/} & per-station-day picks (stage 1) \\
\code{.../pyocto/pyocto\_\{vm\}\_\{year\}.csv} & associated events (stage 2) \\
\code{.../pyocto/pyocto\_assignment\_\{vm\}\_\{year\}.csv} & pick$\rightarrow$event assignment (authoritative) \\
\code{.../station\_table/stations\_\{year\}.csv} & per-year station roster (discovered from metadata) \\
\code{.../HypoInv/PHS/UF\{year\}.phs} & HYPOINVERSE phase file (stage 4) \\
\code{.../HypoInv/\{vm\}/UF\{year\}.\{sum,arc,prt\}} & located catalog + errors (stage 5) \\
\code{outputs/reloc/reloc\_\{year\}\_uf[\_\{model\}]/results/} & dt.cc-relocated catalog + links (stage 6) \\
\bottomrule
\end{tabular}
\end{center}
\noindent \code{\{vm\}} = \code{config.PYOCTO\_VELMODEL} = \textbf{kim2011} for current daily-chunked runs;
legacy pre-2026-07 whole-year artifacts on disk are named \code{kim1983}.

\medskip
\noindent\textbf{Inputs} (metadata by kind, 2026-07): waveforms in \code{KS\_KG/ GJ/ NS/ NS\_100hz/} (station
dirs at each root); station tables in \code{data/metadata/stations/\{ks\_kg,gj,ns,kigam\}/} (+ the per-year
derived cache \code{stations/derived/}); instrument responses in \code{data/metadata/responses/}; velocity
model in \code{data/metadata/velocity/}; HYPOINVERSE control inputs (STA/\code{kim*}) in \code{data/hypoinv/}.

%================================================================================
\section{Stage 6: relocation — HypoDD dt.ct + dt.cc}

The 6th ufpipe stage: turn the QC'd absolute-location catalog into a \textbf{double-difference relocated} catalog
for sub-100\,m relative precision.

\begin{quote}\ttfamily\small
python -m ufpipe.run\_pipeline -{}-model original -{}-years 2016 -{}-stage-from relocate -{}-through dtcc -{}-clean-cache
\end{quote}

\code{ufpipe.relocate} (\code{src/ufpipe/relocate.py}) is \emph{self-fed}: it preflights ufpipe's OWN per-year
association, builds the reloc inputs from it (\code{ufpipe.reloc\_inputs} --- SAC store, pyocto tables, station
table, merged archive), then invokes the validated orchestrator
\code{src/ufpipe/reloc\_driver/run\_picker\_reloc.py -{}-skip-build}, which drives the external
HypoDD/xcorr engine. Internal stages (all KS/KG/GJ/NS):

\begin{center}
\small
\begin{tabular}{@{}c>{\raggedright\arraybackslash}p{3.0cm}>{\raggedright\arraybackslash}p{9.2cm}@{}}
\toprule
\# & Stage & What it does \\
\midrule
1 & SAC store & event-idx-keyed native-rate SAC waveforms from the associated picks (\code{event\_sac/}) \\
2 & HYPOINVERSE & absolute location of all UF-box events (kim2011) $\rightarrow$ \code{.sum} \\
3 & QC & \code{uf\_cluster.QC}: keep \code{erh$<$5, erz$<$5, gap$<$270, num$>$5, rms$<$1.0} \\
4 & re-reference & stamp each SAC's origin from the (full-run) HYPOINVERSE \code{.sum} \\
5 & ph2dt & build \code{event.dat} + catalog differential times \code{dt.ct} \\
6 & xcorr (GPU) & cross-correlation differential times \code{dt.cc} (band 5--20 Hz, interp 1000 Hz, cc$\ge$0.7) \\
7 & HypoDD & kim2011, ISTART=2, ISOLV=2 (LSQR), adaptive damping (CND 40--80), HypoDD v2.1beta (MAXDATA=15M) $\rightarrow$ \code{hypoDD.reloc} \\
\bottomrule
\end{tabular}
\end{center}

\begin{keybox}{Relocation outputs (symlinked into the working dir)}
Each run publishes \code{outputs/reloc/reloc\_<year>\_uf[\_<p>]/results/} with symlinks to the external run tree:
\code{hypoDD.reloc.dtcc} (dt.ct+dt.cc), \code{hypoDD.reloc.dtct} (dt.ct-only), \code{HypoInv.full.sum}, \dots
``dt.cc-resolved'' = events keeping $\ge$1 surviving cross-correlation link — the highest-precision subset.
\end{keybox}

\begin{warnbox}{The invariant that matters (see PIPELINE.md)}
Origins flow into dt.cc: \code{rereference} stamps SAC origins from a \code{.sum}, and xcorr stores
$dt=(t_1{+}\text{shift}{-}ot_1)-(t_2{-}ot_2)$ — subtracting those origins. Use the \emph{full-run} HYPOINVERSE
solution QC gated on (never a redundant re-run), or the dt.cc \emph{values} are corrupted. This is enforced by
\code{run\_picker\_reloc.py::inject\_full\_hypoinverse}.
\end{warnbox}

%================================================================================
\section{Robustness \& invariants}

\begin{itemize}[leftmargin=6mm,itemsep=1mm]
\item \textbf{Network growth is automatic.} Stations are \emph{discovered from StationXML + on-disk coverage}
each month; the deployed network for that period is what enters the run. No hard-coded station lists.
\item \textbf{Mixed sampling rates handled.} $>$100 Hz stations (KG/NS at 200 Hz) are anti-alias-lowpassed then
resampled to the pickers' 100 Hz. The anti-alias filter is applied BEFORE down-sampling (never after).
\item \textbf{Velocity model, thresholds, and gates are epoch-invariant by choice} $\Rightarrow$ the catalog stays
internally comparable across years.
\item \textbf{Idempotent \& resumable} at every stage; \code{-{}-stage-from} restarts mid-chain.
\item \textbf{Do not edit the \code{stead} reference run} (it is the baseline). Scripts refuse \code{-{}-model
stead} writes unless \code{-{}-force}.
\end{itemize}

%================================================================================
\section{Troubleshooting / provenance checks}

\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{6.0cm}>{\raggedright\arraybackslash}p{8.5cm}@{}}
\toprule
Symptom & Check \\
\midrule
Detection finds no waveforms & \code{python -c "import ufpipe.stations as s; print(s.build\_year\_table(YEAR).net.value\_counts())"} --- the per-year multi-network table must list stations, and each row's \code{archive} dir must exist. \\
\code{ImportError: ufpipe} / \code{uflib} & \code{pip install -e . -{}-no-deps} in \textbf{both} \code{eqnet} and \code{base}; \code{import ufpipe.config; print(\_\_file\_\_)} must be \code{src/ufpipe}. \\
\code{ModuleNotFoundError: pyocto} & you ran association in \code{eqnet} --- PyOcto lives in \code{base}. Detection $\to$ \code{eqnet}; association $\to$ \code{base}. \\
\code{InternalMSEEDWarning: ...Steim2 failed} & corrupt Steim2 record(s) in the archive (e.g.\ KG.MKL 2010): the samples still decode; the reader collapses the per-record spam into one summary line per station-day and reads anyway. Informational --- the named station-days are the QC signal. \\
GJ/NS station silently yields no picks & mid-day sampling-rate changes (100/200/1000\,Hz) and int32/float64 records refuse to merge --- handled since 2026-07 (rate + dtype unified \emph{before} merge in both readers). \\
\code{relocate} aborts at preflight & ufpipe's own per-year association is missing for that (model, year) --- run \code{ufpipe.detection} (eqnet) then \code{ufpipe.association} (base); the preflight prints the exact commands. \\
Wrong \code{pipeline} imported & \code{ufpipe} is renamed precisely to avoid the collision with the external korea-cluster-relocation \code{pipeline}. Verify \code{ufpipe.config.\_\_file\_\_} is under \code{src/}. \\
Events look over/under-associated & \code{ASSOC\_GATE} vs \code{-{}-strict} (\code{ASSOC\_GATE\_STRICT}); \code{ASSOC\_PICK\_MATCH\_TOL} is the primary knob. \\
GPU not used & inference is GPU-preferred and warns loudly; check the torch/CUDA install (never silently CPU). \\
Sparse early years, few events & expected --- KS/KG-only network (2010--2015) has larger azimuthal gaps; GJ joins 2016, the dense NS array 2017+; the QC gate honestly reflects what the network resolves. \\
\bottomrule
\end{tabular}
\end{center}

\vspace{2mm}\hrule\vspace{2mm}
{\small\color{soft} Companion docs: \code{docs/overview.md}, \code{docs/pipeline.md}, \code{docs/how-to-run.md},
\code{docs/directory-structure.md} · \code{src/ufpipe/README.md} · relocation pipeline:
\code{src/ufpipe/reloc\_driver/PIPELINE.md} + \code{study\_guide.pdf}.}

\end{document}
